Re-fit

### 2022-07-14 scripts/r/04_refit/refit_sc.Rmd
🐛 - fix missing model number in sphyrna refitted models

```{r}
sphyrna_ellioti_dur_cat <- brm(
  duration ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_dur_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)

sphyrna_ellioti_int_cat <- brm(
  intensity ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_int_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)

sphyrna_ellioti_cfo1_cat <- brm(
  cfo1 ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_cfo1_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)

sphyrna_ellioti_cfo2_cat <- brm(
  cfo2 ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_cfo2_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)
sphyrna_ellioti_cf03_cat <- brm(
  cfo3 ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_cf03_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)
```

>>>>

```{r}
sphyrna_ellioti_1_dur_cat <- brm(
  duration ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_1_dur_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)

sphyrna_ellioti_2_int_cat <- brm(
  intensity ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_2_int_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)

sphyrna_ellioti_3_cfo1_cat <- brm(
  cfo1 ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_3_cfo1_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)

sphyrna_ellioti_4_cfo2_cat <- brm(
  cfo2 ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_4_cfo2_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)
sphyrna_ellioti_5_cf03_cat <- brm(
  cfo3 ~
    POS * condition * eff_cont +
    (POS|speaker) + (POS|AFI),
  data = msa_data,
  file = "./data/analyses/models/sphyrna_ellioti_5_cf03_cat.rds",
  cores = 4,
  threads = threading(2, grainsize = 100), 
  backend = "cmdstanr",
  seed = my_seed
)
```
